Unshuffling Permutations

### 2015-09-25 submission.tex
reduce figure

@@

Let $\pi$ be a permutation. For the sake of clarity, we will say that a
bunch of consecutive positions $P$ of $\pi$ is \emph{above} (resp.
\emph{below}) above another bunch of consecutive positions $P'$ in $\pi$
if $\pi(i) > \pi(j)$ (resp. $\pi(i) < \pi(j)$) for every $i \in P$ and
every $j \in P'$. For example, $\sigma_1$ is above $\sigma_2$ (in an
equivalent manner, $\sigma_2$ is below $\sigma_1$) in
Fig.~\ref{subfig:increasing before and above decreasing}, whereas
$\sigma_1$ is below $\sigma_2$ (in an equivalent manner, $\sigma_2$ is
above $\sigma_1$) in Fig.~\ref{subfig:decreasing before and below
increasing}.
  \begin{figure}[t!]
    \centering
    \subfigure[%
      An increasing pattern before and above a decreasing pattern.
    ]{%
      \begin{tikzpicture}
        [
          scale=0.325,
          label/.style={anchor=base}
        ]
        % increasing pattern
        \draw[step=1cm,black!30,ultra thin,fill=black!10] (-0.2,5.8) grid (5.2,11.2);
        \foreach \x/\y in {0/6,1/7,2/8,3/9,4/10,5/11} {
            \draw [fill=black] (\x,\y) circle (0.1);
        }
        % decreasing pattern
        \draw[step=1cm,black!30,ultra thin,fill=black!10] (5.8,-0.2) grid (11.2,5.2);
        \foreach \x/\y in {6/5,7/4,8/3,9/2,10/1,11/0} {
            \draw [fill=black] (\x,\y) circle (0.1);
        }
        % labels
        \node [label] (a) at (1,5) {$a$};
        \node [label] (b) at (4,5) {$b$};
        \node [label] (ap) at (7,-1) {$a'$};
        \node [label] (bp) at (10,-1) {$b'$};
        \node (nu1) at (2.5,4) {$\sigma_1$};
        \node (nu2) at (8.5,-2) {$\sigma_2$};
        % crossings edges
        \draw [line width=1pt]
        (1,7) .. controls +(0,12) and +(0,10) .. (7,4);
        \draw [line width=1pt]
        (4,10) .. controls +(0,12) and +(0,10) .. (10,1);
      \end{tikzpicture}
      \label{subfig:increasing before and above decreasing}
    }% end subfigure
    \qquad\qquad\qquad
    \subfigure[%
      A decreasing pattern before and below an increasing pattern.
    ]{%
    \begin{tikzpicture}
      [
        scale=0.325,
        label/.style={anchor=base}
      ]
      % decreasing pattern
      \draw[step=1cm,black!30,ultra thin,fill=black!10] (-0.2,-0.2) grid (5.2,5.2);
      \foreach \x/\y in {0/5,1/4,2/3,3/2,4/1,5/0} {
          \draw [fill=black] (\x,\y) circle (0.1);
      }
      % decreasing pattern
      \draw[step=1cm,black!30,ultra thin,fill=black!10] (5.8,5.8) grid (11.2,11.2);
      \foreach \x/\y in {6/6,7/7,8/8,9/9,10/10,11/11} {
          \draw [fill=black] (\x,\y) circle (0.1);
      }
      % labels
      \node [label] (a) at (1,-1) {$a$};
      \node [label] (b) at (4,-1) {$b$};
      \node [label] (ap) at (7,5) {$a'$};
      \node [label] (bp) at (10,5) {$b'$};
      \node (nu1) at (2.5,-2) {$\sigma_1$};
      \node (nu2) at (8.5,4) {$\sigma_2$};
      % crossings edges
      \draw [line width=1pt]
      (1,4) .. controls +(0,10) and +(0,12) .. (7,7);
      \draw [line width=1pt]
      (4,1) .. controls +(0,10) and +(0,12) .. (10,10);
      \end{tikzpicture}
      \label{subfig:decreasing before and below increasing}
    }% end subfigure
    \caption{\label{fig:subfig:no (nu_1, nu_2)-edge}%
      Illustration of Lemma~\ref{lemma:at most one edge monotone}.
    }
  \end{figure}

@@

      scale=.9,

@@

      \node (claim edge 1) at (1.5,13.5) {Claim~\ref{claim:(nu_1, nu'_1)-edge}};
      \node (claim edge 1) at (1.5,13) {Claim~\ref{claim:all (nu_1, nu'_1)-edges}};

@@

      \node (claim edge 2) at (4,4) {Claim~\ref{claim:(nu_2, nu'_2)-edge}};
      \node (claim edge 2) at (4,3.5) {Claim~\ref{claim:all (nu_2, nu'_2)-edges}};

@@

      \node (claim edge 1) at (5.5,11.5) {Claim~\ref{claim:(nu_3, nu'_3)-edge}};

@@

      \node (claim edge 1) at (8.5,8.5) {Claim~\ref{claim:(nu_4, nu'_4)-edge}};

@@

  Let $\pi \in S_n$ and $\sigma \in S_k$ be two arbitrary permutations.
  Define
  \begin{align*}
  N_4 &= 2(2n + 2k + 4) + 1  = 4n + 4k + 9 \\
  N_3 &= 2(2N_4 + 2n + 2k + 4) + 1 = 20n + 20k + 45 \\
  N_2 &= 2(2N_3 + 2N_4 + 2n + 2k + 4) + 1 = 100n + 100k + 225 \\
  N_1 &= 2(2N_2 + 2N_3 + 2N_4 + 2n + 2k + 4) + 1 = 1000n + 1000k  + 1325\text{.}
  \end{align*}
  Notice that $N_1, N_2, N_3$ and $N_4$ are polynomial in $n$.
  The crucial properties are that
  (i) $N_1, N_2, N_3$ and $N_4$ are odd integers
  and
  (ii) $N_i > \left(\sum_{i < j \leq 4} 2N_j\right) + 2n + 2k + k$
  for every $1 \leq i \leq 4$.

>>>>

\begin{figure}[t!]
  \centering
  \subfigure[%
    An increasing pattern before and above a decreasing pattern.
  ]{%
    \begin{tikzpicture}
      [
        scale=0.325,
        label/.style={anchor=base}
      ]
      % increasing pattern
      \draw[step=1cm,black!30,ultra thin,fill=black!10] (-0.2,5.8) grid (5.2,11.2);
      \foreach \x/\y in {0/6,1/7,2/8,3/9,4/10,5/11} {
          \draw [fill=black] (\x,\y) circle (0.1);
      }
      % decreasing pattern
      \draw[step=1cm,black!30,ultra thin,fill=black!10] (5.8,-0.2) grid (11.2,5.2);
      \foreach \x/\y in {6/5,7/4,8/3,9/2,10/1,11/0} {
          \draw [fill=black] (\x,\y) circle (0.1);
      }
      % labels
      \node [label] (a) at (1,5) {$a$};
      \node [label] (b) at (4,5) {$b$};
      \node [label] (ap) at (7,-1) {$a'$};
      \node [label] (bp) at (10,-1) {$b'$};
      \node (nu1) at (2.5,4) {$\sigma_1$};
      \node (nu2) at (8.5,-2) {$\sigma_2$};
      % crossings edges
      \draw [line width=1pt]
      (1,7) .. controls +(0,12) and +(0,10) .. (7,4);
      \draw [line width=1pt]
      (4,10) .. controls +(0,12) and +(0,10) .. (10,1);
    \end{tikzpicture}
    \label{subfig:increasing before and above decreasing}
  }% end subfigure
  \qquad\qquad\qquad
  \subfigure[%
    A decreasing pattern before and below an increasing pattern.
  ]{%
  \begin{tikzpicture}
    [
      scale=0.325,
      label/.style={anchor=base}
    ]
    % decreasing pattern
    \draw[step=1cm,black!30,ultra thin,fill=black!10] (-0.2,-0.2) grid (5.2,5.2);
    \foreach \x/\y in {0/5,1/4,2/3,3/2,4/1,5/0} {
        \draw [fill=black] (\x,\y) circle (0.1);
    }
    % decreasing pattern
    \draw[step=1cm,black!30,ultra thin,fill=black!10] (5.8,5.8) grid (11.2,11.2);
    \foreach \x/\y in {6/6,7/7,8/8,9/9,10/10,11/11} {
        \draw [fill=black] (\x,\y) circle (0.1);
    }
    % labels
    \node [label] (a) at (1,-1) {$a$};
    \node [label] (b) at (4,-1) {$b$};
    \node [label] (ap) at (7,5) {$a'$};
    \node [label] (bp) at (10,5) {$b'$};
    \node (nu1) at (2.5,-2) {$\sigma_1$};
    \node (nu2) at (8.5,4) {$\sigma_2$};
    % crossings edges
    \draw [line width=1pt]
    (1,4) .. controls +(0,10) and +(0,12) .. (7,7);
    \draw [line width=1pt]
    (4,1) .. controls +(0,10) and +(0,12) .. (10,10);
    \end{tikzpicture}
    \label{subfig:decreasing before and below increasing}
  }% end subfigure
  \caption{\label{fig:subfig:no (nu_1, nu_2)-edge}%
    Illustration of Lemma~\ref{lemma:at most one edge monotone}.
  }
\end{figure}

@@

Let $\pi$ be a permutation. For the sake of clarity, we will say that a
bunch of consecutive positions $P$ of $\pi$ is \emph{above} (resp.
\emph{below}) above another bunch of consecutive positions $P'$ in $\pi$
if $\pi(i) > \pi(j)$ (resp. $\pi(i) < \pi(j)$) for every $i \in P$ and
every $j \in P'$. For example, $\sigma_1$ is above $\sigma_2$ (in an
equivalent manner, $\sigma_2$ is below $\sigma_1$) in
Fig.~\ref{subfig:increasing before and above decreasing}, whereas
$\sigma_1$ is below $\sigma_2$ (in an equivalent manner, $\sigma_2$ is
above $\sigma_1$) in Fig.~\ref{subfig:decreasing before and below
increasing}.

@@

      scale=.8,

@@

      % SUPPRIMER COMMENTAIRE POUR VERSION LONGUE
      % \node (claim edge 1) at (1.5,13.5) {Claim~\ref{claim:(nu_1, nu'_1)-edge}};
      % \node (claim edge 1) at (1.5,13) {Claim~\ref{claim:all (nu_1, nu'_1)-edges}};

@@

      % SUPPRIMER COMMENTAIRE POUR VERSION LONGUE
      % \node (claim edge 2) at (4,4) {Claim~\ref{claim:(nu_2, nu'_2)-edge}};
      % \node (claim edge 2) at (4,3.5) {Claim~\ref{claim:all (nu_2, nu'_2)-edges}};

@@

      % SUPPRIMER COMMENTAIRE POUR VERSION LONGUE
      % \node (claim edge 1) at (5.5,11.5) {Claim~\ref{claim:(nu_3, nu'_3)-edge}};

@@

      % SUPPRIMER COMMENTAIRE POUR VERSION LONGUE
      % \node (claim edge 1) at (8.5,8.5) {Claim~\ref{claim:(nu_4, nu'_4)-edge}};

@@

  Let $\pi \in S_n$ and $\sigma \in S_k$ be two arbitrary permutations.
  Define
  % \begin{align*}
  % N_4 &= 2(2n + 2k + 4) + 1  = 4n + 4k + 9 \\
  % N_3 &= 2(2N_4 + 2n + 2k + 4) + 1 = 20n + 20k + 45 \\
  % N_2 &= 2(2N_3 + 2N_4 + 2n + 2k + 4) + 1 = 100n + 100k + 225 \\
  % N_1 &= 2(2N_2 + 2N_3 + 2N_4 + 2n + 2k + 4) + 1 = 1000n + 1000k  + 1325\text{.}
  % \end{align*}
  $N_4 = 2(2n + 2k + 4) + 1  = 4n + 4k + 9$,
  $N_3 = 2(2N_4 + 2n + 2k + 4) + 1 = 20n + 20k + 45$,
  $N_2 = 2(2N_3 + 2N_4 + 2n + 2k + 4) + 1 = 100n + 100k + 225$ and
  $N_1 = 2(2N_2 + 2N_3 + 2N_4 + 2n + 2k + 4) + 1 = 1000n + 1000k  + 1325$.
  Notice that $N_1, N_2, N_3$ and $N_4$ are polynomial in $n$.
  The crucial properties are that
  (i) $N_1, N_2, N_3$ and $N_4$ are odd integers
  and
  (ii) $N_i > \left(\sum_{i < j \leq 4} 2N_j\right) + 2n + 2k + k$
  for every $1 \leq i \leq 4$.
